Network Configuration Synthesis with Abstract Topologies

### 2016-11-08 paper/abstraction/appendix.tex
update appendix

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}{Definition}
\newtheorem{lem}[thm]{Lemma}

@@

\begin{lem}
  For any map $m$ and regular expression $r$ over abstract locations, path $p \in \Lang(con(r,m)) \iff f(p) \in \Lang(r)$.
\end{lem}
\begin{proof}
By induction on the structure of $r$

@@

\begin{lem}
  Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$. We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ in the following way:

@@

@@

\begin{lem}
  If, for product graph $PG = (G,s,P)$ with $G=(V,E)$, if we have the following:

@@

  \[ \begin{array}{ll}
    1. & \tilde{n} = b \\
    2. & f_{pg}(n) = N \\
    3. & (m,n) ~ \text{is an edge in the product graph}~ PG \\
    4. & P(n) = P(N) \\
  \end{array} \]

@@

    suppose that $m = (a, q_1, \dots, q_k)$. Then we know that $M = (f(a), q_1, \dots, q_k)$. Also suppose there is some $b$ such that $N = (f(b), s_1, \dots, s_k)$ since $f^{-1}(N) \neq \emptyset$. This means that, since $(a,b)$ is an edge in the concrete topology, so $(f(a),f(b))$ is an edge in the abstract topology. Also we know that $\tilde{N} = f(b)$.

@@

    \begin{easylist}
      & Clearly $\tilde{n} = b$
      & Clearly $f_{pg}(n) = (f(b), s_1, \dots, s_k) = N$
      & For each regular expression $\sigma^A(q_i, f(b)) = s_i$. This means that for each regular expression, $\sigma(q_i, b) = s_i$. It follows that $(m,n)$ is an edge in the product graph by definition.
      & Since the final states are the same for each state $q_i$ of each product graph state, it follows that $P(n) = P^A(f(n)) = P^A(N)$.
    \end{easylist}

>>>>

\newtheorem{thm}{Theorem}[section]
\newtheorem{defn}{Definition}
\newtheorem{lem}[thm]{Lemma}
\newtheorem*{cor}{Corollary}

@@

We compile regular expressions to automata. As a side condition, we ensure that there are no transitions from some state $q$ to the initial state: $\sigma(q,x) = q_0$. This is done by creating another state $q_0'$ with the same transition function as $q_0$ and all other states transition to $q_0'$ instead of $q_0$.

\begin{lem}
  For any map $\Gamma$ and regular expression $r$ over abstract locations, path $p \in \Lang(con(r,\Gamma)) \iff f(p) \in \Lang(r)$.
\end{lem}
\begin{proof}
By induction on the structure of $r$

@@

\begin{lem}
  Consider the PG created from compiling the constraint $p = (t ~\Path~ r_1 ~\Prefer~,\dots, ~\Prefer~ r_k)$ with state machine $M^A_i$ for each $r_i$. We know that, for each $(pfx ~\Path~ r'_1 ~\Prefer~,\dots, ~\Prefer~ r'_k) \in con(p)$ where $r'_i$ is of the form $r \cap \text{end}(L)$ we can constuct state machine $M_i$ for $r'_i$ over the same states in the following way:

@@

\begin{cor}
  foo
\end{cor}

@@

\begin{lem}
  If $f_{pg}(n) = N$, then $P(n) = P^A(N)$.

  \begin{proof}
    Assume $n = (a,q_1,\dots,q_k)$. We know that $f_{pg}(n) = (f(a),q_1,\dots,q_k)$. 
    We also know that $q_i \in F_i \iff q_i \in F^A_i$. 
    By the definition of the preference function $P$, then $P(n) = P^A(N)$.
  \end{proof}

\begin{lem}
  If, for abstract product graph $PG$, if we have the following:

@@

  \[ \begin{array}{ll}
    1. & \tilde{n} = b \\
    2. & f_{pg}(n) = N \\
    3. & (m,n) ~ \text{is an edge in the product graph}~ PG \\
  \end{array} \]

@@

    suppose that $m = (a, q_1, \dots, q_k)$. Then we know that $M = (f(a), q_1, \dots, q_k)$. Also suppose there is some $b$ such that $N = (f(b), s_1, \dots, s_k)$ since $f^{-1}(N) \neq \emptyset$. This means that, since $(a,b)$ is an edge in the concrete topology, $(f(a),f(b))$ is an edge in the abstract topology. Also we know that $\tilde{N} = f(b)$.

@@

    \begin{easylist}
      & Clearly $\tilde{n} = b$
      & Clearly $f_{pg}(n) = (f(b), s_1, \dots, s_k) = N$
      & For each regular expression $\sigma^A(q_i, f(b)) = s_i$. This means that for each regular expression, $\sigma(q_i, b) = s_i$ if $q_i \neq q_{0_i}$. We know that $q_i \neq q_{0_i}$ due to the side condition for automaton construction. It follows that $(m,n)$ is an edge in the product graph by definition.
    \end{easylist}
